Using Distributed Information Stores for Patient-Clinician Health Data Sharing

### 2013-01-15 patient-clinician-workshop/pccworkshop.tex

>>>>

\section{Personal Electronic Sensors}

There has been a surge in popularity of personal electronic sensors as
part of the ``quantified-self'' movement to measure and improve one's health.
Wireless sensors such as the Fit-bit and Nike FuelBand and small and discreet,
yet provide the wearer with a wealth of information about their own activity level.
In particular, wearers have a desire to improve their health and fitness, based on
the feedback they receive from their device.

The measurements from such devices are of particular interest because of the
frequency and granularity of measurement that they perform - showing minute-by-minute updates
throughout the day, with no clinical involvement.

In addition to fitness monitors, the market for quantified self sensors has
expanded into areas of personal health. For example, there are sensors for
measuring blood oxygenation\footnote{SpO2 Blood Oxygenation sensor: \url{http://ispo2.com}},
Heart Rate Variability and Respiratory Rate\footnote{Zensorium Tinke, heart and respiratory rate sensor: \newline \indent \indent \indent \url{http://www.zensorium.com/tinke/}} and
Temperature and Galvanic Skin Response\footnote{BodyMedia Core 2, temperature and GSR sensor: \newline \indent \indent \indent  \url{http://www.bodymedia.com}}.
The diet aspect of weight loss is also covered, by products such as a wireless fork that informs you how long you spent eating\footnote{HapiLabs HapiFork: \newline \indent \indent \indent  \url{http://hapilabs.com/products-hapifork.asp}}.

Currently these products tend to work in isolation, where the readings from a single product
are presented either on the device themselves, or via a smartphone or website. However,
their use could be integrated with clinical care, in order to monitor patients, and to give an
insight into their lifestyle.
